DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-04 paper/evaluation.tex

These increases in inference times in the co-scheduled scenarios are
expected and likely caused by contention in the shared hardware
resources such as the shared L2 cache and/or the DRAM controller.
To further analyze the source of contention, we use hardwawre
performance counters of the processor. Specifically, we measure L2
miss rates of the DNN models first in isolation and then after
co-scheduling another models. If the shared L2 cache is the primary
source of inteference, then the measured L2 miss rates would
increase. Figure~\ref{fig:l2missrate-vs-modelcnt} shows the results.
As can be see in the figure, L2 miss rates are largely unchanged
regardless whether multiple models are co-scheduled or not. This
suggests that the shared L2 cache is not the bottleneck that caused
execution time increases. In other words, DNN models appear to be not
sensitive to the shared L2 cache space. % L2 partitioning is probably
                                % not going to be useful.
Instead, we hypothesize that it is likely caused by the memory
controller---the only other major shared hardware source---where
memory requests from different CPU cores contend, which would result
in increased memory access latency. While some Intel processors
provide uncore hardware counters that can measure average memory
access latency~\cite{ye2016maracas}, we were not able to identify
whether such hardware counters exist in the BCM2837 processor of
Raspberry Pi 3 due to the lack of documentation. Instead, in the next
experiment, we use memory intensive synthetic benchmark to test the
hypothesis.

@@

\subsection{Benchmark Performance}
In order to determine how cache misses affects the performance of the DeepPicar, we test its ability by 
running synthetic benchmarks concurrently with the model. In each experiment, we run a single model on a 
number of cores, and a synthetic benchmark on the remaining idle cores. The effects of the benchmarks can
seen in Figure 9 and Table VI.

>>>>

These increases in inference times in the co-scheduled scenarios are
expected and likely caused by contention in the shared hardware
resources such as the shared L2 cache and/or the DRAM controller.
To further analyze the source of contention, we use hardwawre
performance counters of the processor. Specifically, we measure L2
miss rates of the DNN models first in isolation and then after
co-scheduling another models. If the shared L2 cache is the primary
source of inteference, then the measured L2 miss rates would
increase. Figure~\ref{fig:l2missrate-vs-modelcnt} shows the results.
As can be see in the figure, L2 miss rates are largely unchanged
regardless whether multiple models are co-scheduled or not. This
suggests that the shared L2 cache is not the bottleneck that caused
execution time increases. In other words, DNN models appear to be not
sensitive to the shared L2 cache space. % L2 partitioning is probably
                                % not going to be useful.
Instead, we hypothesize that it is likely caused by the memory
controller---the only other major shared hardware source---where
memory requests from different CPU cores contend, which would result
in increased memory access latency. While some Intel processors
provide uncore hardware counters that can measure average memory
access latency~\cite{ye2016maracas}, we were not able to identify
whether such hardware counters exist in the BCM2837 processor of
Raspberry Pi 3 due to the lack of documentation. Instead, in the next
experiment, we use memory intensive synthetic benchmarks to test the
hypothesis.

@@

\subsection{Effect of Co-scheduling Memory Performance Hogs}

In order to determine how contended DRAM requests affect the DNN
inference timing of the DeepPicar, we use a synthetic memory
intensive benchmark from the IsolBench suite~\cite{Valsan2016}.

we test its ability by  running synthetic benchmarks
concurrently with the model. In each experiment, we run a single model
on a  number of cores, and a synthetic benchmark on the remaining idle
cores. The effects of the benchmarks can seen in Figure 9 and Table
VI.
